### 2024-02-23 ms.qmd
Updates

Behavioural flexibility, i.e. the ability to adjust the behaviour adaptively in response to internal or external changes by problem-solving, innovation, or alterations in one behaviour in favour of another [@brown2010behavioral], is considered crucial for invasion success [@wright2010behavioral; @chapple2012can; @szabo2020can]. In general, species with higher behavioural flexibility are more likely to survive and establish in new habitats, as behaving flexibly enhances their capacity to exploit new resources and face new challenges [@wright2010behavioral; @chapple2012can; @szabo2020can]. For instance, when closely related species of birds were compared, successful invaders showed a higher frequency of foraging innovations [@sol2000behavioural]. According to the adaptive flexibility hypothesis, behavioural flexibility is particularly relevant during introduction, establishment, and spread of the population [@wright2010behavioral; @chapple2012can; @szabo2020can], stages that can involve more than one generation. If behavioural flexibility is adaptive in these different phases, both this trait and the underlining mechanisms are expected to persist through generations in successful invaders. For example, in mammals, birds, reptiles and amphibians, relative brain size is a good predictor of behavioural flexibility and invasive success [@sol2000behavioural; @sol2002behavioural; @sol2008brain; @amiel_smart_2011]. Since the brain is especially sensitive to environmental changes during the early stages of development [@zhu_prenatal_2004] it is possible that the new prenatal environment faced by establishing populations can affect the behavioural flexibility of the new generations [see @jonson1976effect; @lui2017chronic], with a consequent impact on invasion success. As such, we find that studying the effect of developmental conditions on behavioural flexibility can be key to understand and predict the success of invasive species.  
**BETTER LINK**In this scenario, prenatal glucocorticoids (GCs) and thermal environment can be salient factors in the study of behavioural flexibility within the context of invasion biology. GCs are the main group of hormones related to animals’ response towards alterations in homeostasis [@sapolsky_how_2000] that may become relevant when facing new environments and their new thermal conditions [@Crino_2023]. Furthermore, there is evidence that both developmental GCs and thermal environment can impact cognition in different taxa [@jonson1976effect; @zhu_prenatal_2004; @amiel_hotter_2012; @lui2017chronic]. For instance, young Sprague-Dawley rats treated with corticosterone (CORT) - the principal GC in rodents, birds, and reptiles [@Crino_2023] - performed worse than controls in a reversal learning task [@lui2017chronic], while exposure of pregnant guinea pigs to higher temperatures resulted in significant impairments with offspring behavioural flexibility [@jonson1976effect]. In addition, the cognitive effects of both factors are triggered by similar physiological mechanisms intertwined with brain development [@jonson1976effect; @coomber_independent_1997; @zhu_prenatal_2004; @amiel_effects_2017], an aspect that is considered essential in successful invaders [@sol2000behavioural; @sol2002behavioural; @sol2008brain; @amiel_smart_2011].  
Here, we studied the interactive contribution of prenatal temperature and CORT on behavioural flexibility in two species that exhibit distinct outcomes in their roles as invasive species, the delicate skink (_Lampropholis delicata_) and the common garden skink (_L. guichenoti_). These two species are closely related and share similar life history traits [@chapple_know_2011; @chapple_biology_2014], but only _L. delicata_ has been successful in colonising different areas around the globe [@baker1979rainbow; @chapple2013divergent; @chapple2015deliinvLHI]. Some studies have shown differences in personality traits between these two species that can be related to higher behavioural flexibility in _L. delicata_, and are likely key for its invasive success [@chapple_know_2011; @chapple2012can; @bezzina2014does]. However, differences between species in behavioural flexibility and how this trait is affected by the prenatal environment remains unknown. To investigate these effects, we first manipulated CORT levels and incubation temperature in eggs from both species, and then subjected the juveniles to a reversal learning task as a measure of behavioural flexibility [@brown2010behavioral; @szabo2020can]. We predicted that _L. delicata_ would, on average, perform more proficiently in the task that _L. guichenoti_. We also predicted that prenatal CORT and temperature would affect the behavioural flexibility of both species, but that _L. guichenoti_ would be more impacted by the prenatal treatments than _L. delicata_. High prenatal temperatures are considered to improve performance in cognitive tasks in some ectotherms [@amiel_hotter_2012; @amiel_egg_2014; @clark_colour_2014]. For this reason, we predicted that lizardss incubated at higher temperatures would perform better in the learning reversal task. Conversely, we predicted that prenatal CORT would impair learning [@lemaire_prenatal_2000; @zhu_prenatal_2004; @lui2017chronic]. Finally, we expected an interaction between both treatments, with high temperatures mitigating the negative effects of prenatal CORT on the performance of the lizards in the task.

@@

#### Experimental design
We employed juveniles of both species, _L. delicata_ and _L. guichenoti_ that came from a breeding colony kept in the lab. This colony, established in 2019, originates from animals collected in Sydney, likely from similar populations that have become invasive on Lord Howe Island [@chapple2016origin] (details of breeding colony and husbandry in Supplementary Material). To see the effect of prenatal CORT and temperature, eggs were topically supplied with 5µL of CORT dissolved in 70% Ethanol and 30% DMSO ('CORT' treatment) or the same volume of the vehicle ('Control'), and were then incubated at different temperatures ('Cold' -- 23ºC ± 3ºC or 'Hot' -- 30ºC ± 3ºC) until hatching.  
To estimate behavioural flexibility, we examined lizards' performance in a reversal learning task using colour as the main conditioned stimulus and food (frozen small *A. domestica*) as a reward (see @fig-Methods). The learning test was divided in three main phases: there was first a habituation phase where lizards had to learn to eat from white 3D-printed PLA ramps (9 L x 4 W x 5 H cm); then a second step where lizards had to associate the attainability of food with one colour (@fig-Methods Associative task); and finally the reversal task where the colour associated with the attainable food was changed (@fig-Methods Reversal task). In associative and reversal tasks we used three different ramps that were identical in size and shape to the ones for the habituation phase. The colours of the ramps were green, red, and blue, as previous studies demonstrate that squamates can discriminate between these colours [@Baden_Osorio_2019_Vert_vision]. To control for potential colour biases, we assigned one group of lizards to associate the blue ramp with the attainable food in the associative task and the red ramp in the reversal, while the other group was assigned red as correct for the associative and blue for the reversal. In all trials, the position of the feeders was changed randomly to ensure subjects were using colour rather than spatial cues for the association. To avoid the use of chemical cues, we placed the food reward in all three ramps, but in two of them the cricket was covered by small white lids with holes on the top. Lizards were tested once daily between 11 to 12 am, when lizards are active. The training phase lasted 38 days, the Associaive learning task 35, and the Reversal learning task 40 days. We recorded and analysed manually all trials form the learning phases using a standard video player (IINA). PR was the main researcher analysing the data, and was blinded to the lizards' treatment until the end of the analyses. We used as the main variable whether the animal chose the correct ramp first or not. We considered that a choice was made if the head of the lizard was inside the well of one of the ramps. We considered a trial failed if there was no choice in one hour of recording and those trials were considered as 'non data' in the analyses. Here, we analysed the data of the reversal as an index of behavioural flexibility [@brown2010behavioral].

```{r, fig-Methods}
#| label: fig-Methods
#| fig.cap: "Experimental design of early environment manipulation and learning tasks. Stages 1-3 indicate the different phases of the habituation phase. In the associative and reversal tasks, white lids show the ramps where the food reward was not attainable."

@@

We performed the analyses for both species separately. We fitted a total of two different Bayesian multilevel models using the brm function from the brms package (@burkner2017brms) in Quarto (@Allaire_Quarto_2022). We had per each model four parallel chains of 3000 iterations, with a warm up interval of 1000 iterations. We used 'Choice' - whether the individual chose correct (1) or not (0) - as the response variable; and trial, hormone ('CORT' versus 'Control'), incubation temperature ('Cold' versus 'Hot'), and their interaction as fixed factors. Lizard identity was employed as a random intercept, and as a random slope we included the trial within each level of lizard identity. We used the posterior distributions of these models to evaluate differences in learning rate between treatments and species. Learning slopes were obtained using the estimates of the variable trial per each level of the hormone-temperature interaction ('Treatments'); values bigger from zero were considered as evidence of learning, while those less or equal to zero not. We used the pmcmc method to test whether those slopes or the comparissons between treatments (e.g. slope for 'CORT-Cold' lizards minus 'CORT-Hot' lizards) or species were different from zero (two-tailed tests). We considered statistical significance if p-value < 0.05.

@@

Originally, we started with 96 lizards, 48 per species and 12 per treatment per species. However, due to natural mortality (n = 11), no completion of the training stage (n = 1), or no motivation during the learning tasks (n = 3; see above), we ended up with a total of 81 lizards. Final sample sizes per treatment and species are disclosed on @tbl-data.

@@

#| tbl-cap: "Estimates of Associative learning slope for all the different treatments per each task, species and group. Mean shows the aritmetic mean of the estimates obtained from the posteriors of the model, and 95% CI indicates the 95% confidence interval of the mean. All p-values were obtained using pmcmc and test the hypothesis that the mean is equal to zero. In bold, those values that are significant (p-value <0.05)"

@@

We did not find any significant differences between treatments in _L. delicata_ ('Control-Cold' - 'CORT-Cold' = `r format_dec(mean(deli_ControlCold - deli_CORTCold), 3)`, p- value = `r format_dec(pmcmc(deli_ControlCold - deli_CORTCold), 3)`; 'Control-Hot' - 'CORT-Hot' = `r format_dec(mean(deli_ControlHot - deli_CORTHot), 3)`, p- value = `r format_dec(pmcmc(deli_ControlHot - deli_CORTHot), 3)`; 'Control-Hot' - 'Control-Cold' = `r format_dec(mean(deli_ControlHot - deli_ControlCold), 3)`, p-value = `r format_dec(pmcmc(deli_ControlHot - deli_ControlCold), 3)`; 'CORT-Hot' - 'CORT-Cold' = `r format_dec(mean(deli_CORTHot - deli_CORTCold), 3)`, p-value = `r format_dec(pmcmc(deli_CORTHot - deli_CORTCold), 3)`) (see @fig-results) or _L. guichenoti_ ('Control-Cold' - 'CORT-Cold' = `r format_dec(mean(guich_ControlCold - guich_CORTCold), 3)`, p- value = `r format_dec(pmcmc(guich_ControlCold - guich_CORTCold), 3)`; 'Control-Hot' - 'CORT-Hot' = `r format_dec(mean(guich_ControlHot - guich_CORTHot), 3)`, p- value = `r format_dec(pmcmc(guich_ControlHot - guich_CORTHot), 3)`; 'Control-Hot' - 'Control-Cold' = `r format_dec(mean(guich_ControlHot - guich_ControlCold), 3)`, p-value = `r format_dec(pmcmc(guich_ControlHot - guich_ControlCold), 3)`; 'CORT-Hot' - 'CORT-Cold' = `r format_dec(mean(guich_CORTHot - guich_CORTCold), 3)`, p-value = `r format_dec(pmcmc(guich_CORTHot - guich_CORTCold), 3)`) (see @fig-results). When pooled together, we did not find any effect of incubation temperature (_L. delicata_: 'Hot' learning slope - 'Cold' learning slope = `r format_dec(mean((deli_CORTHot + deli_ControlHot) - (deli_CORTCold + deli_ControlCold)),3)`, p-value = `r format_dec(pmcmc((deli_CORTHot + deli_ControlHot) - (deli_CORTCold + deli_ControlCold)),3)`; _L. guichenoti_: 'Hot' learning slope - 'Cold' learning slope = `r format_dec(mean((guich_CORTHot + guich_ControlHot) - (guich_CORTCold + guich_ControlCold)),3)`, p-value = `r format_dec(pmcmc((guich_CORTHot + guich_ControlHot) -(guich_CORTCold + guich_ControlCold)),3)`) or the hormone (_L. delicata_: 'Control' learning slope - 'CORT' learning slope = `r format_dec(mean((deli_ControlCold + deli_ControlHot) - (deli_CORTCold + deli_CORTHot)), 3)`, p-value = `r format_dec(pmcmc((deli_ControlCold + deli_ControlHot) - (deli_CORTCold + deli_CORTHot)), 3)`;_L. guichenoti_: 'Control' learning slope - 'CORT' learning slope = `r format_dec(mean((guich_ControlCold + guich_ControlHot)-(guich_CORTCold + guich_CORTHot)), 3)`, p-value = `r format_dec(pmcmc((guich_ControlCold + guich_ControlHot)-(guich_CORTCold + guich_CORTHot)), 3)`). Finally, we did not find any significant differences when we compared the estimated slopes between species for the reversal task (_L. delicata_ - _L. guichenoti_ = `r format_dec(mean((deli_CORTCold + deli_ControlCold + deli_CORTHot + deli_ControlHot) - (guich_CORTCold + guich_ControlCold + guich_CORTHot + guich_ControlHot)), 3)`, p-value = `r format_dec(pmcmc((deli_CORTCold + deli_ControlCold + deli_CORTHot + deli_ControlHot) - (guich_CORTCold + guich_ControlCold + guich_CORTHot + guich_ControlHot)), 3)`).

@@

The study embarked on unraveling the interactive effects of prenatal temperature and Glucocorticoids (GCs) on behavioral flexibility in two closely related species, the delicate skink (_Lampropholis delicata_) and the common garden skink (_L. guichenoti_). Despite sharing life history traits, only _L. delicata_ has proven successful in colonizing various global regions, and we hypothesized this may be related with higher behavioural flexibility. Furthermore, we expected behavioural flexibility in this species to be less susceptible to the effect of early environment since this trait can be adaptive in several stages of invasion that can involve more than one generation. Nevertheless, we did not find any significant differences between treatments or species when we compared their performance in a reversal task. We found that, on average, all the lizards from the four treatments and the two species learned the reversal task - indicated by estimated slopes that are significantly different from zero - and that they learn, on average, at the same rate. Furthermore, these results were consistent when only those individuals that performed better in the previous associative task were included (see Supplementary material).  
Previous studies have shown that _L. delicata_ is more explorative than _L. guichenoti_, which can be advantageous in some facets of the colonization of new environments [@chapple_know_2011]. However, @bezzina2014does found no differences in learning between the two skinks in an associative learning task. Our results align with the latter study, and suggest that behavioural flexibility does not differ in these species. In addition, we did not find any effect of the treatments on both species. Both results contrast our original predictions, and may indicate that other aspects of their biology are more relevant for _L. delicata_ success as invaders than behavioural flexibility. For instance, the mentioned differences in exploratory behaviour can be the key factor explaining why _L. delicata_ and not _L. guichenoti_ is better at colonising new areas, since exploring more can also enhance the ability to effectively locate novel resources in _L. delicata_ [@chapple_know_2011].  
Our early environment manipulation did not affect the performance of the lizards in the task. We expected CORT to decrease reversal learning abilities and high temperatures to minimize these effects. However, our results show no significant differences between treatments in both species. Our outcome contrast with previous studies that show impairments of high GCs levels in different types of learning tests [@lemaire_prenatal_2000; @zhu_prenatal_2004;  @farrell_developmental_2016], but they are consistent with other experiments where GCs increased or did not impact learning abilities [@szuran_water_1994; @bebus_associative_2016]. More striking is the absence of effect of incubation temperature, since most of the studies in reptiles reported better performance when incubated at higher temperatures in different associative learning and motor tasks [@amiel_hotter_2012; @amiel_egg_2014; @clark_colour_2014]; and those studies that reported cold-incubated lizards to learn faster [@dayananda_incubation_2017; @abayarathna_effects_2020] used incubation temperatures far beyond the natural range in the hot treatment. It could be argued whether our results stem from an insufficient manipulation of the prenatal environment, particularly regarding CORT as it is known to have hermetic effects on learning and neural structure [@du_dynamic_2009; @mcewen_brain_2012]. However, we find these possibilities unlikely for two primary reasons. First, we have observed the effects of the treatments on other traits of the lizards (unpublished data). Conversely, we find more plausible that the effects of the early environment may vary depending on the cognitive task, as evidenced by studies showing variations in the impact of prenatal GCs and temperature on different brain regions [@coomber_independent_1997; @sakata_neural_2000; @lemaire_prenatal_2000]. However, this hypothesis requires further testing, involving assessments of performance in various cognitive tasks together with the neurophysiological effects on different brain nuclei.  
In conclusion, our results indicate that lizards performed the reversal learning task, a measure of behavioral flexibility, at similar rates, with no discernible differences between treatments or species. These findings contrast our initial predictions and suggest that other aspects of _L. delicata_ biology may be more influential for their success as invaders than behavioral flexibility alone. The present study also indicates that prenatal CORT and temeprature do not affect learning abilities in these species. Nevertheless, it remains possible that the effects of the early environment are task-dependent, and future studies should explore performance across different cognitive tasks, as well as the effects of both treatments on brain function.

>>>>

Behavioural flexibility, i.e. the ability to adjust the behaviour adaptively in response to internal or external changes by problem-solving, innovation, or alterations in one behaviour in favour of another [@brown2010behavioral], is considered crucial for invasion success [@wright2010behavioral; @chapple2012can; @szabo2020can]. In general, species with higher behavioural flexibility are more likely to survive and establish in new habitats because behaving flexibly enhances their capacity to exploit new resources and face new challenges [@wright2010behavioral; @chapple2012can; @szabo2020can]. For instance, when closely related species of birds were compared, successful invaders showed a higher frequency of foraging innovations [@sol2000behavioural]. According to the adaptive flexibility hypothesis, behavioural flexibility is particularly relevant during introduction, establishment, and spread of the population [@wright2010behavioral; @chapple2012can; @szabo2020can], stages that can involve more than one generation. If behavioural flexibility is adaptive in these different phases, both this trait and the underlining mechanisms are expected to persist through generations in successful invaders. For example, in mammals, birds, reptiles and amphibians, relative brain size is a good predictor of behavioural flexibility and invasive success [@sol2000behavioural; @sol2002behavioural; @sol2008brain; @amiel_smart_2011]. Since the brain is especially sensitive to environmental changes during the early stages of development [@zhu_prenatal_2004] it is possible that the new prenatal environment faced by establishing populations can affect the behavioural flexibility of the new generations [see @jonson1976effect; @lui2017chronic], with a consequent impact on invasion success. As such, we find that studying the effect of developmental conditions on behavioural flexibility can be key to understand and predict the success of invasive species.  
**BETTER LINK**In this scenario, prenatal glucocorticoids (GCs) and thermal environment can be salient factors in the study of behavioural flexibility within the context of invasion biology. GCs are the main group of hormones related to animals’ response towards alterations in homeostasis [@sapolsky_how_2000] that may become relevant when facing new environments and their new thermal conditions [@Crino_2023]. In addition, there is evidence that both developmental GCs and thermal environment can impact cognition in different taxa [@jonson1976effect; @zhu_prenatal_2004; @amiel_hotter_2012; @lui2017chronic]. For instance, young Sprague-Dawley rats treated with corticosterone (CORT) - the principal GC in rodents, birds, and reptiles [@Crino_2023] - performed worse than controls in a reversal learning task [@lui2017chronic], while cold incubation temperatures in the eastern three-lined skink resulted in significant impairments with behavioural flexibility [@clark_colour_2014]. Moreover, the cognitive effects of both factors are triggered by similar physiological mechanisms intertwined with brain development [@jonson1976effect; @coomber_independent_1997; @zhu_prenatal_2004; @amiel_effects_2017], an aspect that is considered essential in successful invaders [@sol2000behavioural; @sol2002behavioural; @sol2008brain; @amiel_smart_2011].  
Here, we studied the interactive contribution of prenatal temperature and CORT on behavioural flexibility in two species that exhibit distinct outcomes in their roles as invasive species, the delicate skink (_Lampropholis delicata_) and the common garden skink (_L. guichenoti_). These two species are closely related and share similar life history traits [@chapple_know_2011; @chapple_biology_2014], but only _L. delicata_ has been successful in colonising different areas around the globe [@baker1979rainbow; @chapple2013divergent; @chapple2015deliinvLHI]. Some studies have shown differences in personality traits between these two species that can be related to higher behavioural flexibility in _L. delicata_, and are likely key for its invasive success [@chapple_know_2011; @chapple2012can; @bezzina2014does]. However, differences between species in behavioural flexibility and how this trait is affected by the prenatal environment remains unknown. To investigate these effects, we first manipulated CORT levels and incubation temperature in eggs from both species, and then subjected the juveniles to a reversal learning task as a measure of behavioural flexibility [@brown2010behavioral; @szabo2020can]. We predicted that _L. delicata_ would, on average, perform more proficiently in the task that _L. guichenoti_. We also predicted that prenatal CORT and temperature would affect the behavioural flexibility of both species, but that _L. guichenoti_ would be more impacted by the prenatal treatments than _L. delicata_. High prenatal temperatures are considered to improve performance in cognitive tasks in some ectotherms [@amiel_hotter_2012; @amiel_egg_2014; @clark_colour_2014]. For this reason, we predicted that lizards incubated at higher temperatures would perform better in the learning reversal task. Conversely, we predicted that prenatal CORT would impair learning [as seen previously in @lemaire_prenatal_2000; @zhu_prenatal_2004; @lui2017chronic]. Finally, we expected an interaction between both treatments, with high temperatures mitigating the negative effects of prenatal CORT on the performance of the lizards in the task. This may occur for two reasons that are not mutually exclusive: first, an increase in temperature leads to an overall rise in neural density [@amiel_effects_2017], thereby counteracting the impact of CORT [see @lemaire_prenatal_2000; @zhu_prenatal_2004]; and second, the elevated metabolic rate associated with higher temperatures accelerates the metabolism of CORT, resulting in embryos being exposed to CORT for a shorter time.

@@

#### Experimental design
For this study, we used juveniles of _L. delicata_ and _L. guichenoti_ that came from a breeding colony kept in the lab. This colony, established in 2019, originates from animals collected in Sydney, likely from similar populations that have become invasive on Lord Howe Island [@chapple2016origin] (details of breeding colony and husbandry in Supplementary Material). To see the effect of prenatal CORT and temperature, eggs were topically supplied with 5µL of CORT dissolved in 100% Ethanol ('CORT' treatment) or the same volume of the vehicle ('Control'), and were then incubated at different temperatures ('Cold' -- 23ºC ± 3ºC or 'Hot' -- 30ºC ± 3ºC) until hatching.  
To estimate behavioural flexibility, we examined lizards' performance in a reversal learning task using colour as the main conditioned stimulus and food (frozen small *A. domestica*) as a reward (see @fig-Methods). The learning test was divided in three main phases: (1) _habituation_ -  lizards were conditioned to eat from white 3D-printed PLA ramps (9 L x 4 W x 5 H cm); (2) _association_ - lizards were conditioned to associate food with one colour (Fig. 1 Associative task); and (3) _reversal_ - the colour associated with the food was changed (Fig. 1 Reversal task). For the associative and reversal phases we used three different ramps that were identical in size and shape to the ones for the habituation phase. The colours of the ramps were green, red, and blue, as previous studies demonstrate that squamates can discriminate between these colours [@Baden_Osorio_2019_Vert_vision]. To control for potential colour biases, we assigned one group of lizards to associate the blue ramp with the accessible food in the associative task and the red ramp in the reversal, while the other group was assigned red as correct for the associative and blue for the reversal. In all trials, the position of the feeders was changed randomly to ensure subjects were using colour rather than spatial cues for the association. To avoid the use of chemical cues, we placed the food reward in all three ramps, but in two of them the cricket was covered by small white lids with holes on the top. Lizards were tested once daily between 11 to 12 am, when lizards are active. The habituation phase lasted 38 days, the association phase 35, and the reversal phase 40 days. We recorded and analysed manually all trials form the association and reversal phases using a standard video player (IINA). Videos were analysed by one person (P.R.) who was blind to the treatment groups. We used as the main variable whether the animal chose the correct ramp first or not. We considered that a choice was made if the head of the lizard was inside the well of one of the ramps. Lizards were considered to make a correct choice if they chose the ramp with the accessible food first. We scored lizards that chose ramps with inaccessible foods first to have made an incorrect choice. We considered a trial failed if there was no choice in one hour of recording and those trials were considered as ‘non data’ in the analyses. Here, we analysed the data of the reversal as an index of behavioural flexibility [@brown2010behavioral].

```{r, fig-Methods}
#| label: fig-Methods
#| fig.cap: "Experimental design of early environment manipulation and learning tasks. Stages 1-3 indicate the different phases of the habituation phase. In the associative and reversal tasks, white lids show the ramps where the food reward was not accessible."

@@

We performed the analyses for both species separately. We fitted a total of two different Bayesian multilevel models using the brm function from the brms package (@burkner2017brms) in Quarto (@Allaire_Quarto_2022). We had per each model four parallel chains of 3000 iterations, with a warmup interval of 1000 iterations. We used 'Choice' - whether the individual chose correct (1) or not (0) - as the response variable; and trial, hormone ('CORT' versus 'Control'), incubation temperature ('Cold' versus 'Hot'), and their interaction as fixed factors. Lizard identity was employed as a random intercept, and as a random slope we included the trial within each level of lizard identity. We used the posterior distributions of these models to evaluate differences in learning rate between treatments and species. Learning slopes were obtained using the estimates of the variable trial per each level of the hormone-temperature interaction ('Treatments'); values bigger from zero were considered as evidence of learning, while those less or equal to zero not. We used the pmcmc method to test whether those slopes or the comparisons between treatments (e.g. slope for 'CORT-Cold' lizards minus 'CORT-Hot' lizards) or species were different from zero (two-tailed tests). We considered statistical significance if p-value < 0.05.

@@

Originally, we started with 96 lizards, 48 per species and 12 per treatment per species. However, our final sample size was 81 due to natural mortality (n = 11), failure to complete the training stage (n = 1), or if the number of failed tasks (see above) was higher than 15 (n = 3). Final sample sizes per treatment and species are listed in @tbl-data.

@@

#| tbl-cap: "Estimates of Reversal learning slope for all the different treatments per each task, species, and group. Mean shows the arithmetic means of the estimates obtained from the posteriors of the model, and 95% CI indicates the 95% confidence interval of the mean. All p-values were obtained using pmcmc and test the hypothesis that the mean is equal to zero. In bold, those values that are significant (p-value <0.05)"

@@

We found that the learning slopes for all treatments and species were higher from zero, but we did not find any difference between treatments or species. There were not significant differences between treatments in _L. delicata_ ('Control-Cold' - 'CORT-Cold' = `r format_dec(mean(deli_ControlCold - deli_CORTCold), 3)`, p- value = `r format_dec(pmcmc(deli_ControlCold - deli_CORTCold), 3)`; 'Control-Hot' - 'CORT-Hot' = `r format_dec(mean(deli_ControlHot - deli_CORTHot), 3)`, p- value = `r format_dec(pmcmc(deli_ControlHot - deli_CORTHot), 3)`; 'Control-Hot' - 'Control-Cold' = `r format_dec(mean(deli_ControlHot - deli_ControlCold), 3)`, p-value = `r format_dec(pmcmc(deli_ControlHot - deli_ControlCold), 3)`; 'CORT-Hot' - 'CORT-Cold' = `r format_dec(mean(deli_CORTHot - deli_CORTCold), 3)`, p-value = `r format_dec(pmcmc(deli_CORTHot - deli_CORTCold), 3)`) (see @fig-results) or _L. guichenoti_ ('Control-Cold' - 'CORT-Cold' = `r format_dec(mean(guich_ControlCold - guich_CORTCold), 3)`, p- value = `r format_dec(pmcmc(guich_ControlCold - guich_CORTCold), 3)`; 'Control-Hot' - 'CORT-Hot' = `r format_dec(mean(guich_ControlHot - guich_CORTHot), 3)`, p- value = `r format_dec(pmcmc(guich_ControlHot - guich_CORTHot), 3)`; 'Control-Hot' - 'Control-Cold' = `r format_dec(mean(guich_ControlHot - guich_ControlCold), 3)`, p-value = `r format_dec(pmcmc(guich_ControlHot - guich_ControlCold), 3)`; 'CORT-Hot' - 'CORT-Cold' = `r format_dec(mean(guich_CORTHot - guich_CORTCold), 3)`, p-value = `r format_dec(pmcmc(guich_CORTHot - guich_CORTCold), 3)`) (see @fig-results). When pooled together, we did not find any significant effect of incubation temperature (_L. delicata_: 'Hot' learning slope - 'Cold' learning slope = `r format_dec(mean((deli_CORTHot + deli_ControlHot) - (deli_CORTCold + deli_ControlCold)),3)`, p-value = `r format_dec(pmcmc((deli_CORTHot + deli_ControlHot) - (deli_CORTCold + deli_ControlCold)),3)`; _L. guichenoti_: 'Hot' learning slope - 'Cold' learning slope = `r format_dec(mean((guich_CORTHot + guich_ControlHot) - (guich_CORTCold + guich_ControlCold)),3)`, p-value = `r format_dec(pmcmc((guich_CORTHot + guich_ControlHot) -(guich_CORTCold + guich_ControlCold)),3)`) or the hormone (_L. delicata_: 'Control' learning slope - 'CORT' learning slope = `r format_dec(mean((deli_ControlCold + deli_ControlHot) - (deli_CORTCold + deli_CORTHot)), 3)`, p-value = `r format_dec(pmcmc((deli_ControlCold + deli_ControlHot) - (deli_CORTCold + deli_CORTHot)), 3)`; _L. guichenoti_: 'Control' learning slope - 'CORT' learning slope = `r format_dec(mean((guich_ControlCold + guich_ControlHot)-(guich_CORTCold + guich_CORTHot)), 3)`, p-value = `r format_dec(pmcmc((guich_ControlCold + guich_ControlHot)-(guich_CORTCold + guich_CORTHot)), 3)`). Finally, there were not significant differences when we compared the estimated slopes between species (_L. delicata_ - _L. guichenoti_ = `r format_dec(mean((deli_CORTCold + deli_ControlCold + deli_CORTHot + deli_ControlHot) - (guich_CORTCold + guich_ControlCold + guich_CORTHot + guich_ControlHot)), 3)`, p-value = `r format_dec(pmcmc((deli_CORTCold + deli_ControlCold + deli_CORTHot + deli_ControlHot) - (guich_CORTCold + guich_ControlCold + guich_CORTHot + guich_ControlHot)), 3)`).

@@

The study embarked on unravelling the interactive effects of prenatal temperature and Glucocorticoids (GCs) on behavioral flexibility in two closely related species, the delicate skink (_Lampropholis delicata_) and the common garden skink (_L. guichenoti_). Despite sharing life history traits, only _L. delicata_ has proven successful in colonizing various global regions, and we hypothesized this may be related with higher behavioural flexibility. Furthermore, we expected behavioural flexibility in this species to be less susceptible to the effect of early environment since this trait can be adaptive in several stages of invasion that can involve more than one generation. Nevertheless, we did not find any significant differences between treatments or species when we compared their performance in a reversal task. We found that, on average, all the lizards from the four treatments and the two species learned the reversal task - indicated by estimated slopes that are significantly different from zero - and that they learn, on average, at the same rate. Furthermore, these results were consistent when only those individuals that performed better in the previous associative task were included (see Supplementary material).  
Previous studies have shown that _L. delicata_ more readily explores novel environments than _L. guichenoti_, which can be advantageous during colonization [@chapple_know_2011]. However, Bezzina et al. [@bezzina2014does] found no differences in learning between the two skinks in an associative learning task. Our results align with the latter study and suggest that behavioural flexibility does not differ between these species. In addition, we did not find any effect of the treatments on both species. Both results contrast our original predictions and may indicate that other aspects of their biology are more relevant for _L. delicata_ success as invaders than behavioural flexibility. For instance, the mentioned differences in exploratory behaviour can be the key factor explaining why _L. delicata_ and not _L. guichenoti_ is better at colonising new areas, since exploring more can also enhance the ability to effectively locate novel resources in _L. delicata_ [@chapple_know_2011].  
Our early environment manipulation did not affect the performance of the lizards in the task. We predicted that prenatal CORT treatment would decrease reversal learning abilities and that high temperatures would minimize these effects. However, our results show no significant differences between treatments in both species. Our outcome contrast with previous studies that show impairments of high GCs levels in different types of learning tests [@lemaire_prenatal_2000; @zhu_prenatal_2004;  @farrell_developmental_2016], but they are consistent with other experiments where GCs increased or did not impact learning abilities [@szuran_water_1994; @bebus_associative_2016]. More striking is the absence of effect of incubation temperature, since most of the studies in reptiles reported better performance when incubated at higher temperatures in different associative learning and motor tasks [@amiel_hotter_2012; @amiel_egg_2014; @clark_colour_2014]. Furthermore, those studies that reported cold-incubated lizards learn faster [@dayananda_incubation_2017; @abayarathna_effects_2020] used incubation temperatures far beyond the natural range in the hot treatment. In some systems, exposure to CORT during development has hermetic effects on  learning and neural structures [@du_dynamic_2009; @mcewen_brain_2012]. For example, in Sprague–Dawley rats, exposure to high doses of CORT, but not low doses, reduced density of immature neurons and cell proliferation and in the dentate gyrus [@DOSEneurobrummelte2010chronic]. We know that prenatal CORT treatment affects  other traits in both species of lizards used in this experiment (unpublished data). However, it is possible that prenatal CORT treatment affects tissues differently. Conversely, we find more plausible that the effects of the early environment may vary depending on the cognitive task, as evidenced by studies showing variations in the impact of prenatal GCs and temperature on different brain regions [@coomber_independent_1997; @sakata_neural_2000; @lemaire_prenatal_2000]. These hypotheses are not mutually exclusive and could be tested in future experiments using multiple doses of prenatal CORT treatment, assessing learning using multiple cognitive tasks, and by measuring the neurophysiological effects on different brain nuclei.  
In conclusion, our results indicate that lizards performed the reversal learning task, a measure of behavioral flexibility, at similar rates, with no discernible differences between treatments or species. These findings contrast our initial predictions and suggest that other aspects of _L. delicata_ biology may be more influential for their success as invaders than behavioral flexibility alone. The present study also indicates that prenatal CORT and temperature do not affect learning abilities in these species. Nevertheless, it remains possible that the effects of the early environment are task-dependent, and future studies should explore performance across different cognitive tasks, as well as the effects of both treatments on brain function.
